Extracting The Power of Dependent Types

### 2021-07-16 paper.tex
bugfix in sierpinski, add colors to urls and citations
Minor fixes in the intro (and bib file)

\documentclass[sigplan,anonymous,review]{acmart}

@@

\usepackage{agda}
\usepackage{newunicodechar}
\usepackage[final]{listings}
\lstset{
    basicstyle=\small,
}

@@

There are two common approaches to language embedding: deep and shallow.
A shallow embedding defines a language in terms of functions and operators
of the host language.  Programs in a shallowly-embedded language are programs
in the host language, so they are immediately runnable; types of the embedded
language are types of the host language, so the host typechecker is used for
checking embedded programs.  The downside of this approach is that we cannot
easily get the representation of embedded programs.

@@

\item We demonstrate this approach by a concrete example: an embedding
  of (a subset of the) PostScript language into Agda
  (\secref{embedding}). We give several examples of PostScript
  programs written in our embedding, and demonstrate how to statically
  enforce properties such as the absence of stack underflows,
  termination, and functional correctness.

>>>>

\documentclass[sigplan,screen,anonymous,review]{acmart}

@@

\usepackage{agda}
\usepackage{newunicodechar}
\usepackage[final]{listings}
\lstset{
    basicstyle=\small,
}
\usepackage{microtype}

@@

There are two common approaches to language embedding: deep and shallow.
A shallow embedding defines a language in terms of functions and operators
of the host language.  Programs in a shallowly-embedded language are programs
in the host language, so they are immediately run\-nable; types of the embedded
language are types of the host language, so the host typechecker is used for
checking embedded programs.  The downside of this approach is that we cannot
easily get the representation of embedded programs.

@@

\item We demonstrate this approach by a concrete example: an embedding
  of a subset of the PostScript language into Agda
  (\secref{embedding}). We give several examples of PostScript
  programs written in our embedding, and demonstrate how to statically
  enforce properties such as the absence of stack underflows,
  termination, and functional correctness.
